A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-18 main.tex
Write description on reductions.

@@

\begin{definition}[Reduction]
\begin{align*}
    & (\lambda x:\tau.M) N \longrightarrow_\beta M[x \mapsto N] \\
    % & (\Pi x:\tau.\sigma) M \longrightarrow_\gamma \sigma[x \mapsto M] \\
    & \TBL_\alpha (\TB_\alpha M)\longrightarrow_\blacklozenge M \\
    & (\Lambda \alpha.M) \epsilon \longrightarrow_\Lambda M[\alpha \mapsto \epsilon]
\end{align*}
And take a minimum compatible relationship on terms.

    $ M \longrightarrow M'$ iff 
    $ M \longrightarrow_\Lambda M' $, $ M \longrightarrow_\blacklozenge M' $ or $ M \longrightarrow_\beta M' $.
\end{definition}

>>>>

% 演算子の結合順序

% 自由変数

@@

\begin{definition}[Reduction]
There are three reduction rules ($\longrightarrow_\beta, \longrightarrow_\blacklozenge, \longrightarrow_\Lambda$) in \LMD.
Congruence rules which are omitted from the defnition.
\begin{align*}
    & (\lambda x:\tau.M) N \longrightarrow_\beta M[x \mapsto N] \\
    % & (\Pi x:\tau.\sigma) M \longrightarrow_\gamma \sigma[x \mapsto M] \\
    & \TBL_\alpha \TB_\alpha M \longrightarrow_\blacklozenge M \\
    & (\Lambda \alpha.M)\ \epsilon \longrightarrow_\Lambda M[\alpha \mapsto \epsilon]
\end{align*}
We write $ M \longrightarrow M'$ iff $ M \longrightarrow_\beta M'$, $ M \longrightarrow_\blacklozenge M'$, or $ M \longrightarrow_\Lambda M'$.
\end{definition}

$\longrightarrow_\beta$ is normal $\beta-$reduction in lambda calculus.
$\longrightarrow_\blacklozenge$ means that when a quoted code is unquoted, it become the original code.
$\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
where $\epsilon$ is substituted to the stage variable.
There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
$\%_\alpha$, the symbol for CSP, is disappeared when $\epsilon$ is substituted to $\alpha$.
$\TB_\alpha$ and $\TBL_\alpha$ is disappeared in the same way as $\%_\alpha$.
